% What's the problem?
SPORES is a protocol that provides a file transfer service that does not rely 
on a central service but provides strong privacy guarantees.

% Why is it a problem? Research gap left by other approaches?
% Not really covered: Why is it important? Why care?
Consider that Alice wants to share a file with Bob.
She uploads the file to \enquote{the Cloud} (someone else's computer) and sends 
a link to Bob.
Bob fetches the file from the third-party storage.
This allows the third party to infer much information.
SPORES changes this.

% What's the approach? How to solve the problem?
Alice has several devices (laptop, smartphone, etc.) with varying 
online--offline patterns, we call these devices her device squad.
The squad knows which device has which files and each device of the squad has a 
model of the other devices' online--offline patterns.
Alice's devices can coordinate the sending of the file.
Similarly, Bob also has a device squad, and his squad can coordinate receiving 
the file.
Instead of Alice giving Bob a link to the file in the Cloud, Bob gives Alice a 
route where the destination is his squad (\ie the \emph{set} of Bob's devices).

% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?
At the core of our proposal lies a stateless, probabilistic onion-routing 
protocol called SPOR\@.
SPOR relies on a set-based mix-header format based on Sphinx~\cite{Sphinx} (we 
dubb this extension SphinxES, for Sphinx Extended for Sets).
Given an algorithm for secure peer sampling, a probabilistic model of node 
availability, SPOR will populate the layers of SphinxES with sets of devices to 
reliably deliver packets from one set of devices to another over a network of 
mix-nodes with high churn.

This yields several interesting properties, among others: SPOR can provide 
connections over a network of unreliable devices, unlike Tor's network of 
dedicated, always online devices; SPOR removes the weakest-link bandwidth 
problem present in Tor, sets of nodes at each layer provides a wider path and 
thus more bandwidth; at the same time, SPOR still provides privacy guarantees 
en par with Tor.

